%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {SW Engineering Intern} % Job title
    {Inova LLC - Mobile and Web Development Corporation} % Organisation
    {Alexandria EG, UAE, KSA} % Location
    {July 2023 - Oct 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Frontend using Flutter/Dart Android and IOS mobile apps, State management using 
        (provider \& Riverpod) packages, data-flow controllers.}
        \item {Backend using Firebase, Firestore, and Postman RESTful APIs.}
        \item {Integration teamwork brings together project managers, UX/UI designers, backend developers, and Flutter team through virtual and on-site meetings.}
        \item {\textbf{Technical Skills:} Meet tasks deadlines using Native features, Flutter packages e.g.:(http, image picker,uuid, dio, ..,etc)., and common platforms, like: Firebase, Bitbucket, Figma, Postman, Jira as an Agile project management tool, and Slack.Including CI/CD maintenance, localization, dark mode, app environments:( development, staging, production), and introducing flavors.}
        \item {\textbf{Soft Skills:} Teamwork, Time Management, Communication, Presentation skills.}
      \end{cvitems}
    }

\end{cventries}


%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
    \cventry
      {SW Engineering Intern} % Job title
      {AIT Systems Corporation for web design, cloud hosting, and development services.} % Organisation
      {Alexandria EG} % Location
      {Aug 2022 - Sep 2022} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Web development, security principles, visual design, and mobile app in the \textbf{\textcolor{cyan}{\href{https://github.com/AsmaaJAH/Smart-Parking-System}{SPS}}} smart parking system project.}
          \item {Coordinating with AASTMT, ITIDA, and Alex University. using: (Dart, Flutter WebView, MySQL, WordPress, Photoshop CS6 in logo/icons design).}
    \end{cvitems}
      }
  
  \end{cventries}
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
    \cventry
      {GRIP(Graduate Rotational Internship Program)} % Job title
      {The Sparks Foundation} % Organisation
      {Remotely, India and Singapore} % Location
      {Feb 2022 - April 2022} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Python codes to collect, analyze data, Build \& tune models, Colab ML Classification, Neural Network, and AI Search Algorithms. }
    \end{cvitems}
      }
  
  \end{cventries}

%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
    \cventry
      {Engineering intern } % Job title
      {AMOC "Alexandria Mineral Oils Corporate"} % Organisation
      {Egypt} % Location
      {Sep 2021} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Two Weeks intern at the SW, IT, and Network Department.}
    \end{cvitems}
      }
  
  \end{cventries}


%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
    \cventry
      {Six weeks Of C++ Language Training} % Job title
      {The Arab Academy for Science, Technology and Maritime Transport (AASTMT)} % Organisation
      {Egypt} % Location
      {2014} % Date(s)
      {
        \begin{cvitems} % Description(s) of tasks/responsibilities
          \item {Prepared for the ACM and IOI ( International Olympiad in Informatics for secondary school students).}
    \end{cvitems}
      }
  \end{cventries}
