%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Skills}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvskills}

%---------------------------------------------------------
  \cvskill
    {Fundamentals} % Category
    {OOP, Data Structures and Algorithms, Design patterns, SOLID principles, OS, Database, Web Security Basics.} % Skills
%---------------------------------------------------------
\cvskill
{Languages} % Category
{ Dart, C/C++, SQL, Python, Java, HTML/CSS, UML, DML, ERD, MATLAB, VHDL.} % Skills

%---------------------------------------------------------
\cvskill
{Platforms} % Category
{ Flutter cross-platform, mySQL DBMS, Firebase/Firestore Platform, Agile project management tool ( Jira). } % Skills

%---------------------------------------------------------
\cvskill
{Libraries} % Category
{Flutter Packages(shared preferences, sqflite, http, animation,..etc), OpenCV, Matplotlib, Scikit Learn, PyTorch, NumPy, Keras.} % Skills

%---------------------------------------------------------
\cvskill
{SW Tools} % Category
{Git ( GitHub, Bitbucket), Eclipse, PyCharm, Colab, Visual Studio Code, Android Studio, WordPress, Slack, AutoCad.} % Skills
%---------------------------------------------------------
\cvskill
{GUI Tools} % Category
{Figma, PhotoShop CS6, Qt Designer.} % Skills

%---------------------------------------------------------
\cvskill
{HW Tools} % Category
{Arduino, PCB designing using: Altium, Proteus.} % Skills

%---------------------------------------------------------
\cvskill
{Simulation Tools} % Category
{Cisco Packet Tracer, WireShark analyzer, Multisim, Modelsim, LabVIEW.} % Skills

%---------------------------------------------------------
  \cvskill
    {Miscellaneous} % Category
    {Linux(Ubuntu using Oracle VM VirtualBox), Shells ( cmd, PowerShell), LaTeX (Overleaf), Microsoft Office and Master ICDL.} % Skills

%---------------------------------------------------------
  \cvskill
    {Soft Skills} % Category
    {Problem-solving, Prioritizing, Creativity, Presentation skills, Straightforwardness.} % Skills

\end{cvskills}
