%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Volunteering}
\begin{itemize}[noitemsep, topsep=0pt,left=1pt, label=-]
 {\small
    \item \descriptionstyle {A member of IEEE Solid-State Circuits Society Alex Students' Chapter, Machine learning team, 2020 - 2023.}
     \item \descriptionstyle {A software and AI trainee at Torpedo technical team in FOE, Alex Uni in 2021.}
    \item \descriptionstyle {	Participated in AI and ML summer sessions (offered by: CSE department, Faculty of Engineering, Alex.Uni.)}
    \item \descriptionstyle {  Certificated after finishing the tasks of the Machine Learning course offered by Stanford University.}
    \item \descriptionstyle { A Participant in PCB sessions at Alex Engineers Syndicate.}
    \item \descriptionstyle { An E-Web school session participant (EWeb student chapter), a volunteer at Resala org (2013-2021), \& Naqaa Nanotechnology member (2014).}
    \item \descriptionstyle { Participated in ICNLP presentation skills sessions including using (Photoshop CS6) and (Filmora Video Editing).}

    \item \descriptionstyle { A researcher in the “Science Geeks” project in "Bibliotheca Alexandrina" for the scientific theater in 2015.
    \item An active participant in YESBU in "Bibliotheca Alexandrina" and the LYM from 2014 until the end of 2015.}
    \item \descriptionstyle { Teaching "Quran and the biographies of Sahabah", creating innovative educational games for the junior.}
    \item \descriptionstyle { \entrypositionstyle {\textbf{Initiatives:}} founder of the “Change Lives “ association aimed at better education by sharing jobs and scholarships.
    }}
\end{itemize}